---
title: "Sentiment Analysis"
output: html_document
---
```{r}
library(here)
library(dplyr)
library(tidytext)
library(tidyr)
library(knitr)
library(ggplot2)
```


Sentiment analysis allows us to use standard lexicons to explore the 
sentiments expressed in texts. 


```{r}
load(here("data/quakersaints_trimmed.rda"))
load(here("data/quakersaints_long.rda"))
```

Will will use the long data (one word per line). In this data you should also
have a row number variable and a variable that defines which
chapter/story/section the word is in.  We will be using those variables
to help us to explore sentiments in the text.

```{r}
bing <- get_sentiments("bing")
bing |> inner_join( quakersaints_long, by = "word", multiple = "all" ) -> qs_bing
```

```{r}
table(qs_bing$sentiment)
table(qs_bing$sentiment) |> prop.table() |>round(2)
```

Overall the lannguage is more negative than positive.

```{r}
table(qs_bing$sentiment, qs_bing$younger) |> prop.table(2) |> round(2)
```

If we compare the stories deemed suitable for younger children to the
others, the children's are more negative.

```{r}
table(qs_bing$sentiment, qs_bing$section_type) |> prop.table(2) |> round(2)

```

Interestingly the stories are more negative than the other materials.

This does tend to support the idea that the epigraphs are more flowery.

Based on this, I'm going to redo the earlier comparisons of young and old with
just stories.

```{r}
qs_bing |> filter(section_type == "Story") -> qs_stories_bing
table(qs_stories_bing$sentiment, qs_stories_bing$younger) |> 
  prop.table(2) |> round(2)
```

The results are essentially the same. 

How much variation is there from story to story? 

```{r}
table( qs_stories_bing$title, qs_stories_bing$sentiment) |> 
  prop.table(1) |> round(2)
```

This is a lot; is there a better way to display this?

```{r}
 qs_stories_bing |> group_by(title) |> 
  summarize(Positive = round(sum(sentiment == "positive")/n(), 2)) |>
  arrange(Positive) |> kable()
```


Visualizing this would be better.   This is one possible way.  
For yours make sure to add labels.  In this case I might also want to
add a line highlighting .5 or to change the tick marks to help visualize
that.  Do what makes sense for your data. 

```{r fig.height=5}
 qs_stories_bing |> group_by(title) |> 
  summarize(Positive = round(sum(sentiment == "positive")/n(), 2)) |>
  arrange(Positive) |> 
  ggplot(aes(x=reorder(title, Positive), y =Positive)) +
  geom_point(size = 4) +
   geom_segment(aes(x=title, xend=title, y=0, yend=Positive)) +
  coord_flip()


```


Another thing to look at will be how sentiments change during the stories.

How do we have to fix this to make it meaningful?


```{r}
 qs_stories_bing |> 
  
ggplot( aes(row_number, sentiment, fill =title)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~title, ncol = 2, scales = "free_x")
```






On your own do the same kind of analysis but using the afinn lexicon.  
You will have to think about what needs to change when you have numbers
rather than just positive/negative.

